---
title: "QF 202 Quiz 3"
date: "2/18/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1

1. Download stock price data using package `quantmod` for AAPL and GOOG from 2015-01-01 to 2021-01-01, and compute their daily **log return**.

```{r}
# Do not include install.packages() commands
library(quantmod)

name_list <- c("GOOG",  "AAPL")
getSymbols(name_list, from = "2015-01-01", to = "2021-01-01", src = "yahoo")

#head(diff(log(AAPL$AAPL.Adjusted)))
#head(diff(log(GOOG$GOOG.Adjusted)))

AAPL_log_daily_rtn <- dailyReturn(AAPL, type = "log")
GOOG_log_daily_rtn <- dailyReturn(GOOG, type = "log")

head(AAPL_log_daily_rtn)
head(GOOG_log_daily_rtn)

```
2. Please adapt the recitation code to construct a linear model using returns from part 1. Explain why you chose AAPL as explanatory and GOOG as response or vice-versa. Print out the regression summary.

```{r}
plot(as.vector(GOOG_log_daily_rtn),as.vector(AAPL_log_daily_rtn) )
regression.relation=lm(GOOG_log_daily_rtn~AAPL_log_daily_rtn)
summary(regression.relation)

plot(regression.relation)

#chose google as the predictive var because its more affected by the tech secotrs and the correlation is pos



```

3. Write down the null hypothesis and alternative hypothesis of a significance test about the relationship between AAPL daily log return and GOOG daily log return. What is the p-value of the test? State your conclusion. 
```{r}
t.test(as.vector(AAPL_log_daily_rtn),as.vector(GOOG_log_daily_rtn), alternative = "two.sided" , conf.level = 0.95)
#p val 0.71, no significant correlation

#Ho: there is no predictive relationship
#HA: there is a predictive relationship between google and apple
```





# Do not forget to compile the source file to a report before you submit it on Canvas!
