---
title: "QF 202 Quiz 7"
date: "3/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(2021)
```

# Question 1

1. Please analyze the following code. Run the code to generate a sequence of length = 10000. 

```{r}
n = 10000
epsilon=rnorm(n,sd=0.5)
rt = epsilon[-n]-0.4*epsilon[-1]

```

Please write down in the provided space the name of the model, its formula dynamics using the numerical values of the parameters.


r_t = a_t - 0.4*a_{t-1}
a_t~N(0,0.5) for all t


2. Fit the data to the model using `arima()` function, and the proper order. Display the results from `tsdiag()` and state your observations.
```{r}
model = arima(x = rt, order = c(0, 0, 1))
tsdiag(model)

#we have not evidence against the null (all tested lags are zero), we can assume the series is stationary and modeled correctly
```

3. Output 5-step prediction using the estimated model. 

```{r}
predict(model, n.ahead = 5)
```


# Do not forget to compile the source file to a report before you submit it on Canvas!
