---
title: "QF 202 Quiz 2"
date: "2/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1

1. Download stock price data using package `quantmod` for AMZN and WMT from 2015-01-01 to  2021-01-01

```{r}
library(quantmod)

name_list <- c("AMZN", "WMT")
getSymbols(name_list, from = "2015-01-01", to = "2021-01-01", src = "yahoo")

```
2. Calculate **simple returns** for both stocks and name them as _x_ and _y_ respectively, print `head(x)` and `head(y)`.

```{r}
s_returns1 = diff(AMZN$AMZN.Adjusted)
s_returns2 = diff(WMT$WMT.Adjusted)

n <- length(s_returns1)
x <- as.vector(s_returns1[2:(n-1)])

n <- length(s_returns2)
y <- as.vector(s_returns2[3:n])
head(cbind(x, y))

head(x)
head(y)
```

3. Remove NA from the data and calculate the covariance matrix and correlation matrix, what can you say about them?

```{r}
cov(x, y)
cor(x, y)

cov(cbind(x, y))
cor(cbind(x, y))

amzn_ret = diff(AMZN$AMZN.Adjusted)[-1]
wmt_ret = diff(WMT$WMT.Adjusted)[-1]


data <- cbind(amzn_ret, wmt_ret)
#data

cov(data)
cor(data)

```


# Question 2

The following code generates a sequence, take a look at the code and inteprete the structure of this sequence. Write down the recursive relationship. Bonus: State the name of this sequence.

```{r}
a = 1
b = 1
x = c(a,b)
x

for (i in 1:100)
{
  temp <- a+b
  a<-b
  b<-temp
  x <- append(x, b)
}
x
```

Your answer:
add the last two numbers together to make the next. fibonacci




# Do not forget to compile the source file to a report before you submit it on Canvas!
