---
title: "QF202_Hw1"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this assignment please compile a word document using Rmarkdown and submit. You could also submit a pdf file.
Problem 1. (15 points)You are asked to invest in one of 3 equities. Suppose we know the future distribution of returns is:
         
          Return     Probability
Stock A     6%            0.6
           -3%            0.4 

Stock B     3%            0.7
           -1%            0.3

Stock C    45.43%         0.5
            -50%          0.5

(a)Calculate the expected return for each stock.
    
    To calculate the expected return we multiply the returns by their respective probabilities
    then adding the returns together.

(b)Compute the variance of the returns for each stock.
   
    To compute the variance we subtract from the expected value squared the expected value of 
    the return squared.

(c)Which choice you would make and argue why.

```{r}
#a Expectation
  #stock a
  0.06*0.6+(-0.03)*0.4

  #stock b
  0.03*0.7+(-0.01)*0.3
  
  #stock c
  0.4543*0.5+(-0.50)*0.5
  
#b Variance
  #stock a
  (((0.06)^2)*0.6 + ((-0.03)^2)*0.4) - (0.06*0.6 + (-0.03)*0.4)^2
  
  #stock b
  (((0.03)^2)*0.7+((-0.01)^2)*0.3) - (0.03*0.7+(-0.01)*0.3)^2
  
  #stock c
  (((0.4543)^2)*0.5+((-0.50)^2)*0.5) - (0.4543*0.5+(-0.50)*0.5)^2
  
#c
  
  # I choose stock b because its returns are very consistant and I can expect long term positive  returns


```
Problem 2. (30 points )Let $X$ and $Y$ be two random variables with the following joint density function:

$$
 f(x,y) = \begin{cases} 
                c(x+y), &\text{0 < x < 2,   0 < y < 1}\\
                 0, &\text{otherwise}\\
                 \end{cases}
$$

(a)Calculate the value that makes this function a proper joint probability density function


 $$\int_{0}^{1} \int_{0}^{2} c(x+y) dx dy = c \int_{0}^{1}\int_{0}^{2}(x+y)dxdy$$

 $$=c\int_{0}^{1}(\frac{x^2}{2}+yx)|^2_0$$

$$= 2 c (y+\frac{y^2}{2})|^1_0 = 2c+\frac{2c}{2} = 1\\$$

$$c = \frac{1}{3}$$





(b)What is the marginal density $f(y)$? Use the value found in part(a)

  $$
  f_Y(x,y) = \int_{0}^{2}\frac{1}{3}(x+y)dx\\
  =\frac{1}{3}\int_{0}^{2}\text{x+y }dx =\frac{1}{3}(\frac{x^2}{2} + yx)|^2_0=\frac{1}{3}(2+2y)
  $$

(c)Calculate the density of $X|Y=y$ for some $y∈(0,1)$

$$
f_{X|Y}(x,y) = \frac{f_{X,Y}(x,y)}{f_Y(y)}
$$

(d)What is the expected value of $X$ given $Y=y$? $(E[X|Y=y])$
$$
E[X|Y=y]=\int_{-\infty}^{\infty}x\frac{f_{X,Y}(x,y)}{f_Y(y)}dx\\
\int_{0}^{2}x\frac{(x+y)}{(2+2y)}dx=\frac{1}{2+2y}\int_{0}^{2}x^2+yxdx\\
=\frac{1}{2+2y}(\frac{x^3}{3}+\frac{yx^2}{2})|^2_0= \frac{1}{2+2y}(\frac{8}{3}+\frac{4y}{2})\\
=\frac{\frac{8}{3}+2y}{2+2y}
$$

(e)What is E[X|Y]? What is the difference between the answer to this problem and the answer in (d)?

$$
E[X|Y=y]=\frac{\frac{8}{3}+2y}{2+2y}
$$
In part d the Y has a given range of values, while in question e the Y variable does not have given valuse. However, this does not change the expectation of the function.

Bonus. (10 points)Given the same setting from Problem 2, answer the following:
(a)What is the marginal density $f(x$)? What about conditional density of $Y|X=x$?
$$
  f_X(x,y) = \int_{0}^{1}\frac{1}{3}(x+y)dy\\
  =\frac{1}{3}\int_{0}^{1}\text{x+y }dy =\frac{1}{3}(\frac{y^2}{2} + yx)|^1_0=\frac{1}{3}(x+\frac{1}{2})
$$

(b)Are $X$ and $Y$ independent? Why?
$$
f_X(x,y) \cdot  f_Y(x,y) = f_{X,Y}(x,y)\Leftrightarrow  independent\\
\frac{1}{3}(x+\frac{1}{2})\cdot \frac{1}{3}(2+2y)\neq \frac{1}{3}(x+y)
$$

(c)Calculate the unconditional expectation E[X]
$$
E[X]=\int xf_X(x,y)dx\\
E[X]=\int_{0}^{2}x\frac{1}{3}(x+\frac{1}{2})dx = \frac{1}{3}\int_{0}^{2}x^2+\frac{x}{2}dx=\frac{1}{3}(\frac{x^3}{3}+\frac{x^2}{4})|^2_0\\
=\frac{1}{3}(\frac{8}{3}+\frac{4}{4})=\frac{11}{9}
$$

Problem 3 (40 points) Assume $X_1,X_2,···,X_n$ iid follow $N(μ,σ2)$.

(a)State the distribution of the r.v.$Y_n=∑^n_{i=1}Xi/n$ and give the value of its parameters.

  

(b)Plot the probability density functions of random variables $X_1$ and different $Y_n$ on the same plot. Use $μ= 2,σ= 1$. Plot the Yn density for n= 5,10,30,50.
```{r}

pdf1 <- function(x){
                n = 1
                (1/( (1/sqrt(n)) * (sqrt(2*pi)) )) * exp( (-1/2) * ((x-2)/sqrt(1/n))^2)
}

pdf5 <- function(x){
                n = 5
                (1/( (1/sqrt(n)) * (sqrt(2*pi)) )) * exp( (-1/2) * ((x-2)/sqrt(1/n))^2)
}

pdf10 <- function(x){
                n = 10
                (1/( (1/sqrt(n)) * (sqrt(2*pi)) )) * exp( (-1/2) * ((x-2)/sqrt(1/n))^2)
}

pdf30 <- function(x){
                n = 30
                (1/( (1/sqrt(n)) * (sqrt(2*pi)) )) * exp( (-1/2) * ((x-2)/sqrt(1/n))^2)
}

pdf50 <- function(x){
                n = 50
                (1/( (1/sqrt(n)) * (sqrt(2*pi)) )) * exp( (-1/2) * ((x-2)/sqrt(1/n))^2)
}


plot(pdf1, -1, 5, col=1, type='l', ylim = range(0,2.75), ylab = 'PDF')
plot(pdf5, -1, 5, col=2, type='l', ylim = range(0,2.75), add = TRUE)
plot(pdf10, -1, 5, col=3, type='l', ylim = range(0,2.75), add = TRUE)
plot(pdf30, -1, 5, col=6, type='l', ylim = range(0,2.75), add = TRUE)
plot(pdf50, -1, 5, col='blue', type='l', ylim = range(0,2.75), add = TRUE)

```

(c)By Central Limit Theorem, construct a new r.v. Z that approximates N(0,1)using                   $X_1,X_2,···,X_n$, for $n→+∞$. To do this please write code that:
    
    (a) GenerateX1,X2,...,Xn.
```{r, cache = TRUE}
    Z <- function(n){
          result <- rnorm(n, 0, 1)
    }
```
    
```{r, cache = TRUE}
    hist(Z(100), -1, 1, breaks = 200)
```
    
```{r, cache = TRUE}
    hist(Z(1000), -1, 1,col = 2, breaks = 200)
```
    
```{r, cache = TRUE}
    hist(Z(100000), -1, 1, col = 3, breaks = 200)
    
```
    
  
    (b) Calculate Z for that n value. Do this sequentially to obtain a sequence of Z values. Then     plot this sequence where the ordinate(x axis) is n and the corresponding abscissas(y axis)       are Z values.Finally add a horizontal line for the value of μ on the same plot.

```{r}
Zn <- list()
N <- 1000
for( i in c(0:N)){
  #print('i')
 # print(i)
  Zn[i] <- list(Z(i))
  #print('zni')
  #print( Zn[i])
  
}
#Zn[1]
ZnMean <- lapply(Zn[c(1:N)], mean)
ZnMean <- unlist(ZnMean)
#ZnMean

plot(ZnMean, xlab = 'Trials', ylab = 'Z Mean', ylim = range(-1:1))
abline(0, 0, col ='red')

ZnVar <- lapply(Zn[c(1:N)], var)
ZnVar <- unlist(ZnVar)

plot(ZnVar, xlab = 'Trials', ylab = 'Z Var', ylim = range(0:2))
abline(1, 0, col ='red')

```














Problem 4. (15 points)In this problem, you need to calculate the values empirically. We toss a fair coin ( P(“Head”)= 0.5) repeatedly. Please decide on an appropriate number of replications of the experiment.

(a)Estimate the expected value of the number of tosses to obtain the first “Head”

  We are running 100000 trials, where we toss a coin (rbinom(1, 1, 0.5)) until we get a 1, then    we average all the runs we have
  
```{r, echo=TRUE}
runs <- c()

for(y in 1:10000){
  loops = 0
  i = 0
      while (i == 0) {
        i = rbinom(1, 1, 0.5)
        loops = loops + 1
      }
    runs <- append(runs,loops)
  }
  #runs
  mean(runs)
  #converge on 2
  
```

(b)Estimate the expected value of the number of tosses to obtain three “Heads”. What is the expected number of“Tails”to get three “Heads”
```{r, echo=TRUE}
runs <- c()

for(y in 1:10000){
  loops = 0
  i = 0
      while (i < 3) {
        i = i + rbinom(1, 1, 0.5)
        loops = loops + 1
      }
    runs <- append(runs,loops)
  }
  #runs
  mean(runs)
  #converge on 6
  
```

(c)What are the theoretical values of the expectations in parts (a) and (b)?
  $E[X]= 1/p$ geometric, find prob of something happening first time
  1/0.5 = 2

  $E[X] = r/p$, r is the number of successes
  3/0.5 = 6



