---
title: "QF202 Homework 3"
author: "Leonid Maksymenko"
date: "3/26/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Problem 1. (20 points)** For this problem, use the Yahoo! Finance website (http://finance.
yahoo.com/) or use the quantmod package. Choose any equity you want. Download 5 years worth
of daily data for the equity you chose from January 1, 2016 to December 31, 2020. Please pay
attention to when the data actually starts and ends.

**(a)** Make a time series plot of the daily close prices (if you downloaded data from Yahoo! Finance,
use the Adj. Close column). Please include a title and labels for each of the axes in the plot.

```{r}
library('quantmod')
library(ggplot2)
getSymbols(c('GME'), from = "2016-01-01", to = "2020-12-31", src = "yahoo")
gme_initial <- GME
GME_df <- as.data.frame(gme_initial$GME.Adjusted)

ggplot(GME_df, aes(x = row.names(GME_df), y= GME.Adjusted, group = 1, color = 0)) +
  theme_bw() + theme(legend.position = "none") +
  geom_line() + ggtitle('GME Adj. Close 2016-01-01 -- 2020-12-31') +
  xlab('Date') + ylab('Price') #+ scale_x_discrete(breaks = 0) +
  #scale_y_discrete(breaks = c('5','10','15','20','25'))

```


**(b)** Using the adjusted close prices, compute the corresponding series of log returns. Make a
histogram and a time series plot of the returns. Report the summary statistics using the
command summary.

```{r}
GME_log_daily_rtn <- dailyReturn(gme_initial, type = "log")
hist(GME_log_daily_rtn, col = 'red', xlab = 'Daily Return %', main = 'GME Daily Returns 2016/01/01 - 2020/12/31')
plot(GME_log_daily_rtn, col = 'red', xlab = 'Daily Return %', main = 'GME Daily Returns 2016/01/01 - 2020/12/31')
summary(GME_log_daily_rtn)
```


**Problem 2. (30 points)** Using the log returns computed in Problem 1, do the following:

**(a)** Use R’s acf function to plot the first 30 lags of the autocorrelation function.

```{r}
acf(GME_log_daily_rtn, lag.max = 30)
```

**(b)** Provide the values of the first 5 lags of the autocorrelation function.

```{r}
acf(GME_log_daily_rtn, lag.max = 5, plot = FALSE)
```

**(c)** Use the PACF function to plot the partial autocorrelations. Based on the plot what is the
recommended order of an AR model.

```{r}
pacf(GME_log_daily_rtn, lag = 100)
pacf(GME_log_daily_rtn, lag = 100, plot = FALSE)
#lag 30 seems to be the most significant, order 9 in next highest
```

**Problem 3. (40 points)**

**(a)** Using the ARIMA function and the order p you determined in previous problem fit an AR(p)
model to the returns.

```{r}
GME_arima <- arima(GME_log_daily_rtn, order = c(30,0,0))
GME_arima
```

**(b)** Now use the built in function ar in R. Using criteria of your choice produce two models as
outputted by the ar function.

```{r}
AME_ar_1 <- ar(GME_log_daily_rtn, order = 35)
AME_ar_2 <- ar(GME_log_daily_rtn, order = 9)
AME_ar_1
AME_ar_2
```

**(c)** Download the same equity data from 2021 from January 1 until January 31. This is your test
data. For each of the models you developed use the predict function to predict returns for
the next 21 days. There should be 21 trading days in Jan 2021. For each model calculate the
mean square error of the prediction by calculating:
$$
\frac{1}{21}\sum_{i=1}^{21} \left (\mathrm{Observed\:return_i}\:-\:\mathrm{Predicted\:return_i} \right )^2.
$$


```{r}
getSymbols(c('GME'), from = "2021-01-01", to = "2021-01-31", src = "yahoo")
GME_predict <- GME
GME_log_daily_rtn_predict <- dailyReturn(GME_predict, type = "log")

#AME_ar_1 <- ar(GME_log_daily_rtn, order = 35, newdata = GME_log_daily_rtn_predict)
#AME_ar_2 <- ar(GME_log_daily_rtn, order = 35, demean = FALSE, newdata = GME_log_daily_rtn_predict)

ar_1_predict <- predict(AME_ar_1, n.ahead = 19)
ar_2_predict <- predict(AME_ar_2, n.ahead = 19)
ar_1_predict[[1]]
ar_2_predict[[1]]

ar_1_error <- sum((ar_1_predict[[1]] - as.numeric(GME_log_daily_rtn_predict))^2)/19
ar_2_error <- sum((ar_2_predict[[1]] - as.numeric(GME_log_daily_rtn_predict))^2)/19
#ar1 error
ar_1_error
#ar2 error
ar_2_error

```
**(d)** Which model is best from the prediction perspective. Explain.

The models are nearly identical. So nether model would be better even though the lags are different.
