---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

Leonid Maksymenko

```{r setup, include=FALSE, warning=F}
knitr::opts_chunk$set(echo = TRUE)
library(forecast)
library(tseries)
library(TSA)
library(quantmod)
library(fUnitRoots)
library(lubridate)
library(pracma)
```

##Problem 1

```{r}
#A
#model
sim = arima.sim(
      model = list(order = c(4,0,0), 
                   ar = c(-0.9598, 
                          -0.9612, 
                          -0.8503, 
                          0.0412
                          )),
      n = 1826,
      sd = 1, 
      mean = 0
      )

#show stationary
adf.test(sim, alternative = "stationary")
```

```{r}
#B
acf(sim)
pacf(sim)
```
The PACF chart for the AR model indicates that the model has a order of 3. The ACF for AR models is not useful as it does not present a distinct cutoff point.

```{r}
#C
auto.arima(sim)
arima(sim, order = c(4,0,0))
#benchmark
#since the models are based on arbitrary random data simply comparing how close our predicted model is to the model we initially created should suffice
arimapred = c(-0.9692,  -0.9773,  -0.8674,  0.0322) 
ar = c(-0.9598, -0.9612,-0.8503,0.0412)
ar - arimapred
#0.0094 0.0161 0.0171 0.0090
```
The predicted arima model was more accurate than the auto.arima and fairly accurate over all.

##Problem 2

```{r}
#
#model
sim1 = arima.sim(
      model = list(order = c(0,0,4), 
                   ma = c(sqrt(3), 
                          sqrt(3), 
                          sqrt(3), 
                          0.9)),
      n = 1826,
      sd = 1, 
      mean = 0
      )

#show stationary
adf.test(sim1, alternative = "stationary")

#show invertible
Mod(polyroot(c(1,
               sqrt(3), 
               sqrt(3), 
               sqrt(3), 
               0.9)))
#all roots > 1 => invertible

#B
acf(sim1)
pacf(sim1)

#C
auto.arima(sim1)
arima(sim1, order = c(0,0,4))
arimapred1 = c(1.7483,  1.7477,  1.7453,  0.9182) 
ma = c(sqrt(3),sqrt(3),sqrt(3),0.9)
ma- arimapred1
#-0.01624919 -0.01564919 -0.01324919 -0.01820000
```
The ACF chart for an MA model shows its order. In this case the ACf indicates that the model has an order of 4 which is correct. The PACF for MA is not useful in identifying its order as it slowly tapers off.
The predicted arima model was more accurate than the auto.arima and fairly accurate over all.


```{r}
aic.matrix = function(data, ar_order, ma_order)
{
  AIC_matrix <- matrix(NA, nrow = ar_order+1, ncol = ma_order+1)
  for(i in 0 : ar_order)
  {
    for(j in 0 : ma_order)
    {
      tem <- tryCatch(arima(data, order = c(i, 0, j))$aic, 
                      error = function(cond)
                      {
                        message(cond)
                        message(". AR: ", i, "; MA: ",j)
                        return (NA)
                      }
      )
      
      AIC_matrix[i+1, j+1] <- tem
    }
  }
  AIC_matrix
}
```
##Problem 3

```{r}
#a
sim2 = arima.sim(
      model = list(order = c(4,0,4), 
                   ar = c(-0.9598, 
                          -0.9612, 
                          -0.8503, 
                          0.0412
                          ),
                   ma = c(sqrt(3), 
                          sqrt(3), 
                          sqrt(3), 
                          0.9)),
      n = 1826,
      sd = 1, 
      mean = 0
      )

adf.test(sim2, alternative = "stationary")

acf(sim2)
pacf(sim2)
eacf(sim2)

```
The ACf has no clear cutoff.
The PACF also has no clear cutoff.
The EACF Starts to make a solid prediction around the AR 4-5 point and begins to give returns on MA 4, however, they only become significant at MA 5-7.

```{r}
#b
#matrix = aic.matrix(sim2,10,10)
#matrix
#which(Reshape(rank(na.omit(matrix))<8, 11)==T, arr.ind = T) -1
```
          [,1]     [,2]     [,3]     [,4]     [,5]     [,6]     [,7]     [,8]     [,9]    [,10]    [,11]
 [1,] 6663.331 6226.910 6226.224 6084.093 5895.859 5877.562 5874.266 5813.881 5724.752 5688.405 5690.155
 [2,] 6441.731 6227.484 6223.388 5705.245 5687.458 5871.540 5873.262 5567.369 5568.556 5547.893 5689.205
 [3,] 6286.638 6166.499 5717.216 5703.114 5707.969 5667.008 5601.716 5581.017 5569.551 5571.300 5476.643
 [4,] 6025.025 6026.154 5883.452 5751.023 5270.988 5269.642 5271.638 5273.056 5273.562 5275.507 5276.097
 [5,] 6024.918 5817.059 5761.537 5599.453 5269.632 5271.563 5271.522 5273.299 5273.717 5271.640 5271.936
 [6,] 5903.285 5691.886 5693.198 5617.044 5271.630 5273.564 5274.512 5273.402 5274.157 5276.348 5277.275
 [7,] 5882.372 5693.629 5691.349 5535.570 5272.909 5273.100 5272.863 5276.047 5273.358 5273.237 5271.531
 [8,] 5881.303 5675.729 5504.183 5473.720 5273.706 5272.887 5275.492 5272.653 5270.279 5273.353 5270.579
 [9,] 5820.437 5579.180 5504.622 5502.183 5275.704 5270.782 5277.317 5272.178 5274.332 5265.802 5275.825
[10,] 5613.485 5528.032 5525.986 5401.865 5275.332 5271.081 5273.529 5275.263 5272.496 5267.035 5272.459
[11,] 5571.325 5525.334 5527.307 5376.293 5274.467 5273.014 5275.004 5275.572 5267.262 5268.387 5270.148
     
     row col
#[1,]   4   4
[2,]   3   5
[3,]  10   8
[4,]   8   9
[5,]   9   9
[6,]  10   9
[7,]  10  10

The brute force method predicts the model to be AR 4 and MA 4
```{r}
#C
arima(sim2, order = c(4,0,4))#using 4,0,4 since that was our prediced model by the brute force aic
armapred = c(-0.9696,  -0.9691,  -0.8545,  0.0465,  1.7541,  1.7542,  1.7612,  0.9224)
arma = c(-0.9598, -0.9612,-0.8503,0.0412, sqrt(3),sqrt(3),sqrt(3),0.9)
arma-armapred
```
The prediction was over all accurate and lost accuracy when predicting the ma part

##Problem 4

```{r}
getSymbols('TSLA', from = "2016-01-01", to = "2021-01-01", src = "yahoo")

logreturns = dailyReturn(TSLA$TSLA.Adjusted, type = "log")[-1]

adf.test(logreturns)

#p value small => unit root does not exist + stationary

#eacf
eacf(logreturns)


matrix2 = aic.matrix(logreturns, 10, 10)
matrix2
which(matrix2 == min(na.omit(matrix2)), arr.ind = TRUE) -1
# order is AR8,MA9

model2 <- arima(logreturns, order = c(8, 0, 9))
model2

```

           [,1]      [,2]      [,3]      [,4]      [,5]      [,6]      [,7]      [,8]      [,9]     [,10]     [,11]
 [1,] -4768.220 -4766.261 -4767.289 -4768.744 -4767.574 -4766.949 -4766.293 -4765.808 -4763.901 -4761.921 -4761.809
 [2,] -4766.265 -4764.263 -4766.586 -4767.172 -4766.728 -4765.385 -4764.986 -4764.587 -4761.901 -4759.920 -4759.808
 [3,] -4767.170 -4766.143 -4773.996 -4772.346 -4771.362 -4766.046 -4771.845 -4762.673 -4760.589 -4758.257 -4758.578
 [4,] -4767.867 -4766.409 -4772.368 -4770.505 -4768.492 -4771.559 -4770.857 -4768.145 -4768.616 -4768.023 -4765.065
 [5,] -4766.943 -4766.124 -4771.635 -4768.375 -4768.949 -4770.067 -4769.291 -4771.770 -4770.216 -4765.724 -4768.741
 [6,] -4766.437 -4764.869 -4772.476 -4770.275 -4770.189 -4771.933 -4772.643 -4766.353 -4773.180 -4769.494 -4762.947
 [7,] -4765.911 -4764.657 -4773.161 -4772.574 -4772.796 -4774.688 -4770.757 -4764.787 -4771.179 -4769.145 -4771.372
 [8,] -4765.745 -4764.497 -4772.272 -4761.026 -4773.006 -4767.061 -4774.351 -4770.320 -4769.917 -4769.689 -4771.303
 [9,] -4763.998 -4762.520 -4760.515 -4768.440 -4771.813 -4769.748 -4768.748 -4771.556 -4768.294 -4776.800 -4767.422
[10,] -4762.126 -4760.718 -4758.531 -4767.988 -4771.933 -4771.482 -4768.624 -4767.369 -4765.659 -4773.702 -4775.881
[11,] -4762.244 -4760.823 -4758.927 -4765.379 -4769.911 -4761.366 -4767.141 -4770.202 -4769.493 -4776.694 -4773.097

     row col
[1,]   8   9

ar term. -0.3191  0.7142  0.8832  -0.7935  -0.2475  0.1504  0.0806  -0.56  0.3274  -0.666
ma term. -0.8536  0.7444  0.1392  -0.1537  0.0074  0.6439  -0.0257     0.0023
sigma^2 estimated as 0.00127:  log likelihood = 2406.4,  aic = -4776.8

Look like a good model based on the lof likleyhood and low aic.